### 2024-07-22 data-visualization.qmd
20240721 - line chart

>>>>

A bar plot of Tom Brady's fantasy points by season is depicted in @fig-lineChart.

```{r}
#| label: fig-lineChart
#| fig-cap: "Line Chart."

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(player_display_name == "Tom Brady"),
  mapping = aes(
    x = season,
    y = fantasy_points,
    fill = position_group
    )
) +
  geom_line(
    linewidth = 1.5,
    color = "blue"
  ) +
  theme_classic()
```
